{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-23 paper/paper.tex
beautified two equatations

\begin{align*}
e ::= n | x | e op e && c ::= x := e | c;c | if e then c else c | while e do c | fork(c)
\end{align*}

@@

\begin{align*}
c ::= [x := e]^n | c;c | [if e then c else c]^n | [while e do c]^n | [fork(c)]^n
\end{align*}

>>>>

\begin{align*}
e ::= n\ |\ x\ |\ e\ op\ e && c\ ::=\ x\ :=\ e\ |\ c;c\ |\ if\ e\ then\ c\ else\ c\ |\ while\ e\ do\ c\ |\ fork(c)
\end{align*}

@@

\begin{align*}
c\ ::=\ [x\ :=\ e]^n\ |\ c;c\ |\ [if\ e\ then\ c\ else\ c]^n\ |\ [while\ e\ do\ c]^n\ |\ [fork(c)]^n
\end{align*}
